Demography and selection since maize domestication

### 2015-05-18 manuscript.tex
JRI ideas added as comments
more ideas
updates

\dropcap{T}his is the beginning of the article. For now, I will give a
bulleted list of the introduction:
\begin{enumerate}
\item Maize
\item Plant domestication
\item Maize domestication
\item Importance of demography
\item Background selection
\end{enumerate}

@@

>>>>

\dropcap{D}omesticated plant species evolve in a unique fashion
compared to their wild relatives \textcolor{red}{(ref here)}. This
results from both the anthropomorphic nature of selection on
domesticates as well as the characteristics of the domestication
bottleneck that they usually experience \textcolor{red}{(ref here)}.

\textcolor{red}{
This is the beginning of the article. For now, I will give a
bulleted list of the introduction:
\begin{enumerate}
\item Plant domestication
\item Maize
\item Maize domestication
\item Importance of demography
\item Background selection
\end{enumerate}
}

@@

%JRI IDEAS:
% look at SFS of SNPs by GERP score in maize vs teosinte. shift to lower freq. should be seen at lower GERP scores in maize
% discuss our estimates of deleterious mutation rate from B stuff.  these suggest only ~25% of mutations are deleterious, which contrasts results from a standard DFE
% do a standard DFE! this gives us the proportion of mutations in categories of Ns. Can use Eyre-Walker software.
% i think we do need to say something about load. add up GERP scores like Li?
